Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
accuracy
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52675 72bbbca6-d526-0410-a7d9-f06f51895060
add more tables
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52676 72bbbca6-d526-0410-a7d9-f06f51895060
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52677 72bbbca6-d526-0410-a7d9-f06f51895060
add table doc stats
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52679 72bbbca6-d526-0410-a7d9-f06f51895060
results+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52681 72bbbca6-d526-0410-a7

@@

(CHECKLATER-FORMATTING)
1. Baseline - Negligible precision and recall show that the task of detecting sub-segments in complex and there needs to be more improvement in the methodology.

>>>>

As described in the evaluation the techniques were used on a dataset collected over a period of time, for the three language pairs\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The statics of the same are described in the Table below. //

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|r}
\hline
\textbf{System} &  \multicolumn{3}{c|}{\textbf{Statistics} (\%)} \\
\hline
       &   lang(1) Tokens & lang(2) Tokens & Phrases of lang(1) & Phrases of lang(2) \\
\hline
\texttt{Irish(1)---English(2)} & 332 & 379 & 40 & 42 \\
\hline
\texttt{Welsh(1)---English(2)} & 419 & 378 & 64 & 66 \\
\hline
\texttt{Breton(1)---English(2)} & 388 & 379 & 54 & 53 \\
\hline
\end{tabular}
\end{center}
\label{table:accuracy}
\caption{Document Statistics of the annotated data used.}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{System} &  \multicolumn{3}{c|}{\textbf{Accuracy} (\%)} \\
\hline
       &   Irish---English & Welsh---English & Breton---French \\ 
\hline
\texttt{baseline} & 42.76 & 42.16 & 44.07 \\
\hline
\texttt{langid2} & 50.35 & 42.28 & 45.11  \\
\hline
\texttt{langid3} & 57.24 & 45.92 & 43.16 \\
\hline
\texttt{wordlist} & 79.75 & 74.28 & 83.96 \\
\hline
\texttt{bigram} & 81.29 & 65.62 & 76.79 \\
\hline
\texttt{wordlist+bigram} & 85.79 & 72.40 & 88.79 \\
\hline
\end{tabular}
\end{center}
\label{table:accuracy}
\caption{Accuracy of the systems over the three language pairs}
\end{table}

(CHECKLATER-FORMATTING)

The Results clearly show that the baseline has a negligible precision and recall, this means that the task of detecting sub-segments is complex and there needs to be more improvement in the technique. You can see that langid.py is better suited for document classification and that when such varied content is introduced the result is an improvement but not promising. In case of the character bigram prediction technique and the word based chunking method, the results show a significant increase in precision and recall values from the rest. The last in the list is the word based prediction with character backoff, which performs collectively better than the others with a high accurracy margin. \\
